### 2017-01-28 thesis/results/results.tex
tmp commit

Both the metagenes generated from Creighton's data and Fuentes-Mattei's data were not associated with sample \gls{bmi}.

>>>>

Both metagenes generated from Creighton's data and FM's data were able to capture the overall pattern of gene expression of the samples, but did not associate with sample \gls{bmi}/\gls{bmi} status.
One possible reason for this result could be that the obesity associated genetic signatures from Creighton's and FM's study may not have been truly associated with sample \gls{bmi} status, but another clinical variable.
To remove this possibility, obesity associated genetic signature was identified in Creighton's data after controlling for all the clinical variables in the data set.
FM's data set was not used to get obesity associated genetic signature, as no \gls{bmi} information was available for the samples in FM's data.
